\section{Introduction}
\label{s:intro}

At the Large Hadron Collider (LHC), top quarks are copiously produced in
quark--antiquark pairs (\ttbar). This process has been extensively studied in proton--proton collisions at 
$7$ and $8\,\TeV$, and recently at $13\,\TeV$~\cite{TOPQ-2015-09, CMS-TOP-15-003}
centre-of-mass energy.  Measurements of the associated production of \ttbar
with a $Z$ boson (\ttZ) allow the extraction of information about the neutral-current coupling of the top quark.  The production rate of a top-quark pair with a
massive vector boson could be altered in the presence of physics beyond the
Standard Model (SM), such as vector-like quarks~\cite{AguilarSaavedra:2009es,Aguilar-Saavedra:2013qpa}, strongly coupled Higgs bosons~\cite{Perelstein:2005ka} 
or technicolour~\cite{Chivukula:1992ap, Chivukula:1994mn, Hagiwara:1995jx, Mahanta:1996ng, Mahanta:1996qe},
and therefore the measurements of \sttZ and \sttW are important
checks of the validity of the SM at this new energy regime.  
The \ttZ and \ttW
processes have been established by ATLAS~\cite{TOPQ-2013-05} and
CMS~\cite{CMS-TOP-14-021} using the Run-1 dataset at $\sqrt{s} = 8\,\TeV$, with
measured cross sections compatible with the SM prediction and having uncertainties of
$\sim\!\!30\%$.  At $\sqrt{s} = 13\,\TeV$, the SM cross sections of the \ttZ and
\ttW processes increase by factors of $3.5$ and $2.4$, respectively, compared
to $\sqrt{s} = 8\,\TeV$. The cross sections, computed at next-to-leading-order
(NLO) QCD precision, using \MGMCatNLO (referred to in the
following as \MGAMC), are $\sttZ = 0.84\,\text{pb}$ and $\sttW =
0.60\,\text{pb}$ with an uncertainty of $\sim\!\!12\%$~\cite{Frixione:2015zaa, Alwall:2014hca}, primarily due to higher-order
corrections, estimated by varying the renormalisation and
factorisation scales.

This paper presents measurements of the \ttZ and \ttW cross sections using
\lumi of proton--proton ($pp$) collision data at $\sqrt{s} = 13\,\TeV$
collected by the ATLAS detector in 2015.  The final states of top-quark pairs
produced in association with a $Z$ or a $W$ boson comprise up to four isolated,
prompt leptons.\footnote{In this paper, lepton is used to denote electron or
muon, and prompt lepton is used to denote a lepton produced in a $Z$ or $W$
boson or $\tau$-lepton decay.}  Decay modes with two same-sign (SS) charged
muons, or three or four leptons are considered in this analysis.  The analysis
strategy follows the strategy adopted for the $8\,\TeV$
dataset~\cite{TOPQ-2013-05}, excluding the lower sensitivity SS dilepton
channels.  Table~\ref{tab:intro-channels} lists the analysis channels and the
targeted decay modes of the \ttZ and \ttW processes.  Each channel is divided
into multiple analysis regions in order to enhance the sensitivity to the
signal.  Simultaneous fits are performed to the signal regions and selected
control regions in order to extract the cross sections for \ttZ and \ttW
production.  Additional validation regions are defined to check that the
background estimate agrees with the data and are not used in the fit.

\begin{table}[htbp]
\centering
\caption{\label{tab:intro-channels} List of \ttW and \ttZ decay modes and
analysis channels targeting them.\vspace{1ex}} 
\begin{tabular}{cccc}
\toprule
Process & \ttbar decay & Boson decay & Channel\\
\midrule
\multirow{2}{*}{$\ttW$} 
&  $(\mu^{\pm}\nu b) (q\bar{q} b) $ & $\mu^{\pm}\nu$ & SS dimuon\\
& $ (\ell^{\pm}\nu b) (\ell^{\mp}\nu b)$ & $\ell^{\pm}\nu$ & Trilepton\\
\midrule
\multirow{2}{*}{\ttZ} 
& $(\ell^{\pm}\nu b) (q\bar{q} b)$ & $ \ell^{+}\ell^{-}$ & Trilepton\\
& $(\ell^{\pm}\nu b) (\ell^{\mp} \nu b)$ & $ \ell^{+}\ell^{-}$ & Tetralepton\\
\bottomrule
\end{tabular}
\end{table}
